---
title: "Analysis"
author: "Rhi"
date: "19/03/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(here)
```

```{r}
candy_data <- read_csv(here("clean_data/candy_clean.csv"))
```

1.
What is the total number of candy ratings given across the three years. (number of candy ratings, not number of raters. Don’t count missing values)
```{r}
candy_data %>%
  filter(!is.na(response)) %>%
  summarise(num_candy_ratings = n())
```

2.
What was the average age of people who are going out trick or treating and the average age of people not going trick or treating?
```{r}
candy_data %>% 
  drop_na(age) %>% 
  group_by(going_out) %>% 
  summarise(mean_age = mean(age))
```

3.
For each of joy, despair and meh, which candy bar revived the most of these ratings?
```{r}
candy_data %>% 
  group_by(candy) %>% 
  filter(response == "JOY") %>% 
  summarise(top_joy = n()) %>% 
  top_n(1)

candy_data %>% 
  group_by(candy) %>% 
  filter(response == "DESPAIR") %>% 
  summarise(top_despair = n()) %>% 
  top_n(1)

candy_data %>% 
  group_by(candy) %>% 
  filter(response == "MEH") %>% 
  summarise(top_meh = n()) %>% 
  top_n(1)

# candy_data %>% 
#   group_by(response) %>% 
#   summarise(top = n()) %>% 
#   top_n(1, candy)
```

4.
How many people rated Starburst as despair?
```{r}
candy_data %>% 
  filter((candy == "[Starburst]" | candy == "Q6 | Starburst") & response == "DESPAIR") %>% 
  summarise(number_of_people_who_hate_starburst = n())
```

5.
What was the most popular candy bar by this rating system for each gender in the dataset?
```{r}
candy_data_test %>%
  drop_na(gender) %>% 
  group_by(gender) %>% 
  filter(response == "JOY") %>% 
  summarise(n())
```

