---
title: "Homework"
output: html_notebook
---
```{r}
library(tidyverse)
library(lubridate)
library(tsibble)
library(tsibbledata)
library(fable)
```

```{r}
nyc_bikes
names(nyc_bikes)
```
Question 1
```{r}
nyc_bikes_1 <- nyc_bikes %>% 
  mutate(year = year(start_time),
         month = month(start_time),
         date = date(start_time))
```

Question 2
```{r}
nyc_bikes_1 %>% 
  index_by(month) %>% 
  summarise(bike_hire_count = n()) %>% 
  ggplot(aes(month, bike_hire_count)) +
  geom_line() +
  xlab("Date")
```
Shows that the bike hire is seasonal throughout the year, peaking around July/August. This increase likely coincides with the increase in good weather. It gives a general idea of the forecast but it is not very precise. Seeing as the data has multiple bike hires in some days, I would probably only downsample this data to weekly. 

Question 3

```{r}
nyc_bikes_3 <- nyc_bikes_1 %>% 
  index_by(date) %>% 
  summarise(bike_hire_count = n()) 

nyc_bikes_3 %>% 
  ggplot(aes(date, bike_hire_count)) +
  geom_line()
```
This plot shows us that there is a lot more variability within the months than the monthly plot. The fluctuations vary within each which may be due to weather changes, 

Question 4

```{r}
nyc_bikes_4 <- nyc_bikes_3 %>% 
  fill_gaps(bike_hire_count = as.integer(median(bike_hire_count)))

fit <- nyc_bikes_4 %>%
  model(
    snaive = SNAIVE(bike_hire_count),
    mean_model = MEAN(bike_hire_count),
    arima = ARIMA(bike_hire_count)
  )
fit
```
question 5
```{r}
forecast_4m <- fit %>%
  fabletools::forecast(h = "4 months")

forecast_4m %>%
  autoplot(nyc_bikes_4, level = NULL) +
  ggtitle("Forecasts for Bike Hire Count") +
  xlab("Month") +
  guides(colour = guide_legend(title = "Forecast"))
```

question 6 
```{r}
train <- nyc_bikes_4 %>%
  filter_index("2018-01" ~ "2018-09")

fit_test <- train %>%
  model(
    mean_model = MEAN(bike_hire_count),
    arima = ARIMA(bike_hire_count),
    snaive = SNAIVE(bike_hire_count))


forecast_test <- fit_test %>% 
  fabletools::forecast(h = 120)

forecast_test %>%
  autoplot(train, level = NULL) +
    autolayer(filter_index(nyc_bikes_4, "2018-10" ~ .), color = "black") +
    ggtitle("Forecasts for monthly bike hire") +
    xlab("Month") + ylab("Bike Hire") +
    guides(colour = guide_legend(title = "Forecast"))


accuracy_model <- fabletools::accuracy(forecast_test, nyc_bikes_4)

accuracy_model %>% 
  select(-.type) %>%
  arrange(RMSE)
```
Question 7
The forecast doesn't appear to be accurate as it clearly does not follow the trend of the data in the model test so none of the models are a good fit for the data. 
Could potentially ask for more data (I don't really understand the errors enough to test a different model)

Question 8

```{r}
nyc_bikes_1 %>% 
  ggplot(aes(x = start_lat, y = start_long, colour = month)) +
  geom_point() +
  facet_wrap(~ bike_id)
```
Bikes 31681 & 31735 were only used in the first half of the year whereas the otheres were hired more in the 2nd half of the year. 


```{r}
nyc_bikes_1 %>% 
  ggplot(aes(x = end_lat, y = end_long, colour = month)) +
  geom_point() +
  facet_wrap(~ bike_id)
```
Very little change which is unsurprising as the bikes were hired and returned in the same day generally..? 

Question 9
```{r}
library(leaflet)
```
```{r}

bike_hire_map <- leaflet(nyc_bikes) %>%
  addTiles() %>% 
  addMarkers(lng = ~ start_long, lat = ~start_lat,
             clusterOptions = markerClusterOptions()) 

bike_hire_map

```

Question 10
```{r}
bike_hire_map_lines <- leaflet(nyc_bikes) %>%
  addTiles() %>% 
  addMarkers(lng = ~ start_long, lat = ~start_lat,
             clusterOptions = markerClusterOptions()
             ) %>% 
  addPolylines(lng = ~ end_long, lat = ~end_lat)
# Need a for loop to only show the line for the selected pin i think.. but it's too late at night

bike_hire_map_lines
```

