---
title: "Homework Quiz"
author: "Rhi"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1
  Likely overfitting because all the children with have a similar DOB as they are all 6yr olds. Additionally, 

2
  AIC score of 33,559 as the lower AIC score is better

I have two models, the first with: r-squared: 0.44, adjusted r-squared: 0.43. The second with: r-squared: 0.47, adjusted r-squared: 0.41. Which one should I use?

  Should use the first as it has a higher adjusted r-squared despite having a lower r-squared. Meaning that the additional variables in the second model do not enhance the model.
1  No, because the 


1
  You split the data into n folds, then make a model with the data n times using a different fold as the test set and the rest as the training set each time. 

What is a validation set? When do you need one?
  This is an additional subset of data that is not used in test or training and is only used once a final model has been chosen in order to avoid overfitting the data.

Describe how backwards selection works.


Describe how best subset selection works.

It is estimated on 5% of model projects end up being deployed. What actions can you take to maximise the likelihood of your model being deployed?

What metric could you use to confirm that the recent population is similar to the development population?

How is the Population Stability Index defined? What does this mean in words?

Above what PSI value might we need to start to consider rebuilding or recalibrating the model

What are the common errors that can crop up when implementing a model?

After performance monitoring, if we find that the discrimination is still satisfactory but the accuracy has deteriorated, what is the recommended action?

Why is it important to have a unique model identifier for each model?

Why is it important to document the modelling rationale and approach?
```{r}

```

