---
title: "Homework"
output: html_notebook
---
1 MVP

```{r}
library(readr)
library(readxl)
library(openxlsx)
library(dplyr)
library(haven)
library(jsonlite)
```
Read in the state_income_data.csv file using the appropriate function.
```{r}
raw_state_income <- read_csv("data/state_income_data.csv")
```

How do you specify your own column names when using read_csv()?
```{r}
read_csv("data/state_income_data.csv", col_names = c("a", "b", "c"))
```

Read in the cars.csv file and use the col_types() function to ensure you load in:

X1 as character
mpg, cyl, disp, hp as double
vs as logical
```{r}
raw_cars <- ?read_csv("data/cars.csv", col_types = col_logical(vs))
```

Read in the scotland.txt file using the appropriate function.
```{r}
raw_scotland <- read_delim("data/scotland.txt", delim = ";", skip = 2, col_names = c("Rank", "Locality", "Population", "Status", "Council Area"))
```

How do you read text into a one element character vector?
```{r}
vector <- read_file()
```

Read in the steam-200k-sample.csv file. Fix any problems you may encounter.
```{r}
read_csv("data/steam-200k-sample.csv", skip = 4)
```

Read in the historic_eu_payments.tsv file.
```{r}
read_tsv("data/historic_eu_payments.tsv")
```

How do you read lines of text into a multi-element text vector?
```{r}

```

Read in the africa_health_data.dta file using the appropriate method.
```{r}
read_dta("data/africa_health_data.dta")
```

Read in the JSON file from the following url: http://makemeanalyst.com/wp-content/uploads/2017/06/sample_json.txt
```{r}
raw_json_file <- read_file("http://makemeanalyst.com/wp-content/uploads/2017/06/sample_json.txt")
json_file <- parse_json(json_file)

```

2 Extension
A lot of Excel sheets you will encounter will contain more than one sheet. Try to write some code that reads in all the different sheets in the file green_bindle_consulting.xlsx.

[Hint: you will need to write a for loop]
```{r}
read_xlsx("data/green_bindle_consulting.xlsx")
```


