---
title: "Extra Week 1 Qs"
output: html_notebook
---
1 Creating and converting vectors
1.1 Creating vectors
Create five vectors, called my_double, my_integer, my_character, my_factor and my_logcal, each of the appropriate type i.e my_double should be a numeric double, my_integer an integer vector etc. The values in these vectors are up to you.
```{r}
my_double <- c(5.64, 67, 89.4)
my_integer <- c(4L, 87L, 24L)
my_character <- c("Liz", "Craig", "Apple", "Plant")
my_factor <- factor("Hippo", "Giraffe", "Tangerine")
my_logical <- c(TRUE, FALSE, TRUE, TRUE, FALSE)

```

1.2 Checking classes
Check the class of each vector is as you would expect.
```{r}
class(my_double)
class(my_integer)
class(my_character)
class(my_factor)
class(my_logical)
```

1.3 More checking classes
You can use the function is.double to check if my_double is a double vector.
Do similar checks for all of the other vectors. You want to answer to be true each time.
```{r}
is.double(my_double)
is.integer(my_integer)
is.character(my_character)
is.factor(my_factor)
is.logical(my_logical)
```
1.4 Converting
Convert my_double to be the four other types. Each time, look at the vector to see the result and check the class of the result.
```{r}
class(as.integer(my_double))
class(as.character(my_double))
class(as.factor(my_double))
class(as.logical(my_double))
```

1.5 Converting numbers
Create a vector called numbers_character, a character vector with the following values: “4”, “5”, “5”. First convert this vector into integer. Then make a factor vector with the same values. What happens when you convert the factor vector to an integer?
```{r}
numbers_character <- c("4", "5", "5")
numbers_factor <- factor(numbers_character)
as.integer(numbers_character)
as.integer(numbers_factor)
#It shows the levels not the values
```
```{r}

```
2 Using functions and operators
2.1 Fibonacci numbers
Add the next three numbers: 377, 610, 987. For the rest of the questions use this new extended Fibonacci sequence.
```{r}
fib <- c(1, 1, 2, 3, 5, 8, 13, 21, 34, 55, 89, 144, 233)
fib <- append(fib, c(377, 610, 987))
fib
```
Print the sequence out with the highest numbers first.
```{r}
sort(fib, decreasing = TRUE)

```
How many of the elements are even?
```{r}
sum(fib %% 2 == 0)
```
What percent of the elements are even?
```{r}
part <- (sum(fib %% 2 == 0))
whole <- (length(fib))

part/whole*100
```
What is the 10th element of the sequence?
```{r}
fib[10]
```

```{r}
golden_ratio <- (1 + sqrt(5))/2
nth_golden_ratio <- function(n){
  (golden_ratio^(n) - ((1 - golden_ratio)^(n)))/sqrt(5)
}

nth_golden_ratio((1:16))
```

The ratio between two successive elements of the sequence will tend to the golden ratio. Calculate the ratio between each element of the sequence and the one after and check if this is true.

```{r}
1/1
1/2
2/3
3/5

```


3 Functions and Control flow
3.1
Write a function that pre-appends “The answer is:” to any character input, and either returns the number for numbers less than 10, or divides the number by 10 for numbers greater than 10. For anything else return “Invalid input”.
```{r}
my_func <- function(n){
  # ifelse(n < 10, x <- n, ifelse(n >= 10, x <- n / 10, ifelse(class(x) != "numerical", x<- "Invalid input"))
  # append("The answer is:", x)}
  if (n < 10){ 
    x <- n
  return (append("The answer is:", x))
  }
  if (n >= 10){
    x <- (n / 10)
    return(append("The answer is:", x))
  }
  else {
    "Invalid input"
    }


my_func("oh")
```

3.2
Write a function which checks if two vectors have the same elements.
```{r}
c <- c(1, 2, 3, 4, 5)
d <- c(1, 2, 3, 4, 5)
e <- c(6, 7, 8, 9, 10)
check_same <- function(a, b){
  if (a == b){
    "Same"
  } else{
    "Different"
  }
}
check_same(c, e)
```
 
If they have the same elements in the same order, return “Exactly the same”
```{r}

```

If they have the same elements but in a different order, return “The same”

If they don’t have the same elements, return “Different”

3.3
Using the list below:

If the element is greater than length one, go and print out each element of the list individually. Print all the length one character vectors as usual.







