---
title: "Homework - Manual Model Development"
output: html_notebook
---

You are given a set of data on housing sale prices for the last few years in King County (near Seattle) between May 2014 and May 2015. Have a look at the variable definitions on the Kaggle page

Tidy up the data ready for regression:

You might like to think about removing some or all of date, id, sqft_living15, sqft_lot15 and zipcode (lat and long provide a better measure of location in any event).
Have a think about how to treat waterfront. Should we convert its type?
We converted yr_renovated into a renovated logical variable, indicating whether the property had ever been renovated. You may wish to do the same.
Have a think about how to treat condition and grade? Are they interval or categorical ordinal data types?
Check for aliased variables using the alias() function (this takes in a formula object and a data set). [Hint - formula price ~ . says ‘price varying with all predictors’, this is a suitable input to alias()]. Remove variables that lead to an alias.

Systematically build a regression model containing up to four main effects (remember, a main effect is just a single predictor with coefficient), testing the regression diagnostics as you go
splitting datasets into numeric and non-numeric columns might help ggpairs() run in manageable time, although you will need to add either a price or resid column to the non-numeric dataframe in order to see its correlations with the non-numeric predictors.
Hints
houses_tidy_numeric <- houses_tidy %>%
  select_if(is.numeric)

houses_tidy_nonnumeric <- houses_tidy %>%
  select_if(function(x) !is.numeric(x))

houses_tidy_nonnumeric$price <- houses_tidy$price

ggpairs(houses_tidy_numeric)
ggpairs(houses_tidy_nonnumeric)
and the same in subsequent rounds of predictor selection with the resid column.

Remember, if you are not sure whether including a categorical predictor is statistically justified, run an anova() test passing in the models with- and without the categorical predictor and check the p-value of the test.

```{r}
library(tidyverse)
library(GGally)
```

```{r}
house_prices <- read_csv("kc_house_data.csv")
```

```{r}
house_prices %>% 
  summary()

```

```{r}
# removing uneccary variables after checking them out 
# Converted renovated to a logical variable
# Grade it interval as it is a scale
# condition is ordinal 
house_prices_tidy <- house_prices %>% 
  mutate(renovated = ifelse(yr_renovated == 0, 0, 1)) %>% 
  select(-c("id", "date", "sqft_living15", "sqft_lot15", "zipcode", "yr_renovated")) 

```

```{r}
alias(price ~ ., data = house_prices_tidy)
# sqft_basement is an aliased coeficiant (from sqft_living & sqft_above) so I remvoed it

house_prices_tidy <- house_prices_tidy %>% 
  select(-sqft_basement)
```

```{r, warning = F, message F}
house_prices_tidy %>% 
  ggpairs()
```
```{r}
model1 <- lm(price ~ lat + long, data = house_prices_tidy)
summary(model1)
par(mfrow = c(2, 2)) 

# plot
plot(model1)
```

