---
title: "R Notebook"
output: html_notebook
---
```{r}
library(rpart)
library(rpart.plot)
library(tidyverse)
library(janitor)
library(modelr)
library(yardstick)

titanic_set <- read_csv('data/titanic_decision_tree_data.csv')

shuffle_index <- sample(1:nrow(titanic_set))

# shuffle the data so class order isn't in order - need this for training/testing split later on 
titanic_set <- titanic_set[shuffle_index, ]
```

```{r}
tidy_titanic <- titanic_set %>% 
  drop_na(survived) %>% 
  mutate(sex = as.factor(sex),
         survived = factor(survived,
                           levels = c(0, 1),
                           labels = c("no", "yes")),
         class = factor(pclass, 
                         levels = c(1, 2, 3),
                         labels = c("upper class", "middle class", "lower class")),
         embarked = factor(embarked, 
                           levels = c("C", "Q", "S"),
                           labels = c("Cherbourg", "Queenstown", "Southampton")),
         age_status = ifelse(age <= 16, "child", "adult")
         ) %>% 
  select(sex, class, embarked, sib_sp, parch, survived, age_status) %>% 
  drop_na()
```
1.
```{r}

tidy_titanic %>% 
  ggplot(aes(survived)) +
  geom_bar(position = "dodge")

tidy_titanic %>% 
  ggplot(aes(survived, fill = sex)) +
  geom_bar(position = "dodge")

tidy_titanic %>% 
  ggplot(aes(survived, fill = age_status)) +
  geom_bar(position = "dodge")

tidy_titanic %>% 
  ggplot(aes(survived, fill = class)) +
  geom_bar(position = "dodge")

tidy_titanic %>% 
  ggplot(aes(sib_sp)) +
  geom_bar(position = "dodge")
```

```{r}
# get how many rows we have in total to work out the percentage
n_data <- nrow(tidy_titanic)

# create a test sample index
test_index <- sample(1:n_data, size = n_data*0.2)

# create test set
titanic_test  <- slice(tidy_titanic, test_index)

# create training set
titanic_train <- slice(tidy_titanic, -test_index)
```

```{r}
titanic_test %>% 
  tabyl(survived)

titanic_train %>% 
  tabyl(survived)
# Seems balanced
```

```{r}
titanic_fit <- rpart(survived ~ ., 
                     data = titanic_train, 
                     method = 'class')

rpart.plot(titanic_fit, yesno = 2)
```

important vaiables: sex, age, class, sib_sp
what does each node tell you:  are more likely to die
highest chance of surviving? High class women and children without siblings
lowest: male, low class, adults

```{r}
# add the predictions
titanic_test_pred <- titanic_test %>%
                 add_predictions(titanic_fit, type = 'class')
```

```{r}
titanic_test_pred %>% 
  select(sex, class, age_status, sib_sp, pred)
```


```{r}

conf_mat <- titanic_test_pred %>%
              conf_mat(truth = survived, estimate = pred)

conf_mat
```
77 - true negatative (correctly predicited 77 deaths)
28 - true positives (correctly predicited 28 survivors)
8 - false positive (incorrectly predicited 8 survivors)
29 - false negatives (incorrectly predicited 29 deaths)



```{r}
accuracy <- titanic_test_pred %>%
 accuracy(truth = survived, estimate = pred)

accuracy 
```

```{r}
rpart.predict(titanic_fit, newdata=titanic_test[1:3,], rules=TRUE)
```













